---
title: "Tutorial for predicting clinical outcomes of COVID-19 patients"
output: html_document
date: '2022-06-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This tutorial demonstrates how to use the shared models to predict clinical outcomes of COVID-19 patients using olink data of plasma proteins. This tutorial is written in the R programing language. 

To run the models, first we will load the required package:

```{r, message=FALSE}
library(randomForest)
```

We then read the olink data and load the random forrest models.

```{r}
olink = read.csv('test_data.csv')
load('final_models.rda')
```



Applying the models to predict 1) disease progression, 2) viral shedding, 3) memory CD4 response,4) IgG response at day 28 and 5) IgG response at month 7. 

```{r}
pred1 = predict(RFlist[["Info_severitycat"]],olink,type='prob')
pred2 = predict(RFlist[["auc"]],olink,type='prob')
pred3 = predict(RFlist[["mCD4"]],olink,type='prob')
pred4 = predict(RFlist[["D28_IgG"]],olink,type='prob')
pred5 = predict(RFlist[["M7_IgG"]],olink,type='prob')
```

